
Plotting median profiles of fluorescence and physical parameters

```{r}
#Loading packages
library(tidyverse) #data wrangling
library(patchwork) #plotting panels
library(readxl) #read excel files
library(here) #data management, file structure
library(scales)
library(ggpmisc)
```

```{r}
#I'm not quite sure where these come from

#KC10 profiles
k <- read.csv(here("outputs", "kc10_profs_qc1.csv"))

#QU39 profiles
q <- read.csv(here("outputs", "qu39_profs_qc1.csv"))

#Buoy data daily
b <- read.csv(here("files", "2024-07-05.1daySamples.all.csv"))

#bouy data hourly
bh <- read.csv(here("files", "2024-07-19.1hourSamples.all.csv"))

#Wannock daily discharge
r <- read.csv(here("files", "daily_20240705T2210.csv"))

```

```{r}
ctd <- rbind(k, q)
```

```{r}
ctd <- ctd %>% 
  mutate(date = lubridate::ymd(date),
         month = lubridate::month(date)) %>%
  mutate(season = case_when(month == 12 | month == 1 | month == 2 ~ "Winter",
                            month >= 3 & month <= 5 ~ "Spring",
                            month >= 6 & month <= 8 ~ "Summer",
                            month >= 9 & month <= 11 ~ "Autumn",)) %>%
  relocate(season, .after = month)  
  
#Order locations from fjord to shelf
order_loc_seas <- c("Winter", "Spring", "Summer", "Autumn")

#Chemtax - Specify order of phyto groups for figures
ctd <- arrange(mutate(ctd,
                         season = factor(season, levels = order_loc_seas)))


```

```{r}
b_less <- b %>% 
  mutate(date = lubridate::mdy(date)) %>% 
  select(date, year, month, WaterSalinity_QC,
         sal = WaterSalinity_Avg) %>% 
  filter(WaterSalinity_QC == "AV" | WaterSalinity_QC == "")

bh_less <- bh %>% 
  mutate(date = lubridate::mdy_hm(measurementTime)) %>% 
  select(date, year, month, WaterSalinity_QC,
           sal = WaterSalinity_Avg) %>% 
  filter(WaterSalinity_QC == "AV" | WaterSalinity_QC == "")
```

```{r}
r_less <- r %>% 
  mutate(date = lubridate::mdy(Date),
         year = lubridate::year(date)) %>% 
  filter(PARAM == 1) %>% 
  filter(year > 2014) %>% 
  select(date, year, q = Value)
```



```{r}
ctd_stat <- ctd %>%
  group_by(station, season, pres) %>% 
  summarise(med_flu = median(flu, na.rm = T),
            sd_flu = sd(flu, na.rm = T),
            med_s = median(sal, na.rm = T),
            sd_s = sd(sal, na.rm = T),
            med_t = median(temp, na.rm = T),
            sd_t = sd(temp, na.rm = T),
            min_s = min(sal, na.rm = T),
            max_s = max(sal, na.rm = T),
            min_t = min(temp, na.rm = T),
            max_t = max(temp, na.rm = T)) %>% 
  ungroup()

ctd_stat_2m <- ctd_stat %>%
  filter(pres == 2)
```

```{r}
formatter <- function(...){
  function(x) format(round(x, 1), ...)
}
```


```{r}
#Plotting just median fluorescence - caution as trends look very notable, but there is a huge amount of variability at KC10

ggplot() +

  geom_smooth(data = ctd_stat, aes(x = med_flu, y = pres, fill = station, color = station),
              orientation = "y", method = "loess", span = 0.2, se = F,
              alpha = 0.4, size = 2) +
  geom_point(data = ctd_stat, aes(x = med_flu, y = pres, color = station),
              alpha = 0.4, size = 3) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(x = "Fluorescence (ug/L)",
       y = "Depth (m)") +
  scale_y_reverse() +
  ylim(50, 1) +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0),
                     labels = formatter(nsmall = 1)) +
  facet_grid(.~season, scales = "free_x") +
  # ggtitle("Seasonal Profiles") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.07, 0.95),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "profile_season_leoss_both_median.png"),
       width = 20, height = 12, dpi = 300)
```

#So, my previous plot was somewhat misleading. There is a huge amount of variability. This could be interesting temporally though. Plot integrated chlorophyll over the timeseries. Should calibrate sensors, but for now, first approximation. 

I do think there is bad data included here though that needs to be removed - I think I did this though. Yes, 80217 removed. Other issues may remain.

```{r}
#calculating 50m integrated value for each station

int_chl <- ctd %>% 
  select(date, station, flu) %>% 
  group_by(date, station) %>% 
  summarise(int_50 = sum(flu, na.rm = T)) %>% 
  ungroup()
```

```{r}
#Plotting integrated chlorophyll time-series by station. Why are there so many data gaps? NA's in profile, likely at surface.

int_chl %>% 
  ggplot(aes(x = date, y = int_50, color = station)) +
  geom_line(size = 1.5) +
  geom_point(pch = 21, size = 2, fill = "white", stroke = 0.5) +
  ggsci::scale_color_aaas() +
  labs(y = "Int. Flu.") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_flu_int_50.png"),
       width = 16, height = 6, dpi = 300)
```
I like Colleen's idea of plotting data from the same week.
```{r}
#Could try to do this by calculating week of year for each station and joining by station:year:week

week_qu39 <- int_chl %>% 
  filter(station == "QU39") %>% 
  group_by(date) %>% 
  summarise(int_50 = mean(int_50)) %>% 
  ungroup() %>% 
  mutate(year = lubridate::year(date),
         week = lubridate::week(date)) %>% 
  select(year, week, int_qu39_50 = int_50)

week_kc10 <- int_chl %>% 
  filter(station == "KC10") %>% 
  group_by(date) %>% 
  summarise(int_50 = mean(int_50)) %>% 
  ungroup() %>% 
  mutate(year = lubridate::year(date),
         week = lubridate::week(date)) %>% 
  select(year, week, int_kc10_50 = int_50)

int_week <- week_kc10 %>% 
  left_join(week_qu39) %>% 
  mutate(date = (lubridate::ymd( "2013-01-01") +
                   lubridate::weeks(week - 1 ))) %>% 
  pivot_longer(c(int_kc10_50, int_qu39_50), values_to = "int_50",
               names_to = "station")
```




```{r}
#To plot need to convert week back to date somehow


int_week %>% 
  ggplot(aes(x = date, y = int_50, color = station)) +
  geom_line(size = 1.5) +
  geom_point(pch = 21, size = 2, fill = "white", stroke = 0.5) +
  ggsci::scale_color_aaas() +
  labs(y = "Int. Flu.") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_flu_int_50.png"),
       width = 16, height = 6, dpi = 300)
```









```{r}
ctd_stat %>%
  ggplot() +
  geom_smooth(data = ctd_stat, aes(x = med_s, y = pres, fill = station, color = station),
              orientation = "y", method = "loess", span = 0.2, se = F,
              alpha = 0.4, size = 2) +
  geom_point(data = ctd_stat, aes(x = med_s, y = pres, color = station),
              alpha = 0.4, size = 2) +
  geom_ribbon(data = ctd_stat, aes(xmin = med_s - sd_s, xmax = med_s + sd_s,
                                     y = pres, fill = station, color = station),
              alpha = 0.4, size = 0.1) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(x = "Salinity",
       y = "Depth (m)") +
  scale_y_reverse() +
  ylim(40, 1) +
  facet_grid(. ~ season) +
  xlim(22, 35) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "profile_season_leoss_both_sal.png"),
       width = 16, height = 12, dpi = 300)
```

```{r}
ctd_stat %>%
  ggplot() +
  geom_smooth(data = ctd_stat, aes(x = med_t, y = pres, fill = station, color = station),
              orientation = "y", method = "loess", span = 0.2, se = F,
              alpha = 0.4, size = 2) +
  geom_point(data = ctd_stat, aes(x = med_t, y = pres, color = station),
              alpha = 0.4, size = 2) +
  geom_ribbon(data = ctd_stat, aes(xmin = med_t - sd_t, xmax = med_t + sd_t,
                                     y = pres, fill = station, color = station),
              alpha = 0.4, size = 0.1) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(x = "Temp",
       y = "Depth (m)") +
  scale_y_reverse() +
  ylim(40, 1) +
  facet_grid(. ~ season) +
  # ggtitle("Seasonal Profiles") +
  # xlim(22, 35) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "profile_season_leoss_both_temp.png"),
       width = 16, height = 12, dpi = 300)
```

```{r}
ctd_stat %>%
  ggplot() +
  geom_smooth(data = ctd_stat, aes(x = med_flu, y = pres, fill = station, color = station),
              orientation = "y", method = "loess", span = 0.1, se = F,
              alpha = 0.4, size = 2) +
  geom_point(data = ctd_stat, aes(x = med_flu, y = pres, color = station),
              alpha = 0.4, size = 2) +
  geom_ribbon(data = ctd_stat, aes(xmin = med_flu - sd_flu, xmax = med_flu + sd_flu,
                                     y = pres, fill = station, color = station),
              alpha = 0.4, size = 0.1) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(x = "Temp",
       y = "Depth (m)") +
  scale_y_reverse() +
  ylim(40, 1) +
  facet_grid(. ~ season, scales = "free_x") +
  # ggtitle("Seasonal Profiles") +
  # xlim(22, 35) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "profile_season_leoss_both_fluorescence.png"),
       width = 16, height = 12, dpi = 300)
```
```{r}
#Look at seasonal cycle for each station.

ctd %>% 
  filter(pres == 2 & year > 2014) %>%
  group_by(month, station) %>% 
  summarise(med_sal = median(sal),
            sd_sal = sd(sal)) %>% 
  ungroup() %>% 
  mutate(year = 2022,
         day = 15) %>% 
  unite(month, c(year, month, day), sep = "-", remove = F) %>% 
  mutate(month = lubridate::ymd(month)) %>% 
  ggplot(aes(x = month, y = med_sal, color = station)) +
  geom_line(size = 1.5) +
  geom_point(pch = 21, size = 2, fill = "white", stroke = 0.5) +
  geom_ribbon(aes(ymin = med_sal - sd_sal,
                  ymax = med_sal + sd_sal,
                  x = month,
                  color = station,
                  fill = station),
              alpha = 0.4, size = 0.1) +
  scale_x_date(breaks = seq(as.Date("2022-01-01"), as.Date("2022-12-31"),
                            by = "month"),
               date_labels = "%b") +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "climatology_salinity_2m_monthly_median.png"),
       width = 16, height = 6, dpi = 300)
```
```{r}
#Look at seasonal cycle for each station.

ctd %>% 
  filter(pres == 2 & year > 2014) %>%
  ggplot(aes(x = as.factor(month), y = sal, color = station, fill = station)) +
  geom_boxplot(alpha = 0.3) +
  geom_point(aes(color = station, fill = station), 
             position = position_dodge(width = 0.75),
             alpha = 0.4) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "climatology_salinity_2m_monthly_boxplot.png"),
       width = 16, height = 6, dpi = 300)
```



```{r}
#Look at seasonal cycle for each station.

ctd %>% 
  filter(pres == 2 & year > 2014) %>%
  mutate(yday = lubridate::yday(date)) %>% 
  mutate(month_doy = as.Date("2021-12-31") + yday) %>% 
  ggplot(aes(x = month_doy, y = sal, color = station)) +
  geom_point(alpha = 0.5, size = 4) +
  geom_smooth(span = 0.3, size = 2) +
  scale_x_date(breaks = seq(as.Date("2022-01-01"), as.Date("2022-12-31"),
                            by = "month"),
               date_labels = "%b") +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "climatology_salinity_2m_monthly_leoss-3.png"),
       width = 16, height = 6, dpi = 300)
```
```{r}
test <- ctd %>% 
  mutate(yday = lubridate::yday(date)) %>% 
  mutate(month.doy = as.Date("2021-12-31") + yday)
```




```{r}
ctd_dm <- ctd %>% 
  filter(pres == 2 & year > 2014) %>% 
  group_by(date, station) %>% 
  summarise(sal = mean(sal)) %>% 
  ungroup() 

ggplot() +
  geom_point(data = b_less, aes(x = date, y = sal),
             size = 3, alpha = 0.1, color = "blue", fill = "blue", pch = 21) +
  geom_line(data = ctd_dm, aes(x = date, y = sal, color = station), size = 1.5) +
  geom_point(data = ctd_dm, aes(x = date, y = sal, color = station),
             pch = 21, size = 2, fill = "white", stroke = 0.5) +
  ggsci::scale_color_aaas() +
  ylim(15, 32) +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_salinity_2m_raw.png"),
       width = 16, height = 6, dpi = 300)
```

```{r}
ctd %>% 
  filter(pres == 2 & year > 2014) %>% 
  mutate(year = lubridate::year(date)) %>%
  group_by(year, month, station) %>% 
  summarise(med_sal = median(sal, na.rm = T),
            sd_sal = sd(sal, na.rm = T),
            n = n()) %>% 
  ungroup() %>% 
  mutate(day = 15) %>% 
  unite(date, c(year, month, day), sep = "-", remove = F) %>% 
  mutate(date = lubridate::ymd(date)) %>% 
  ggplot() +
  geom_line(aes(x = date, y = med_sal, color = station), size = 1.5) +
  geom_point(aes(x = date, y = med_sal, color = station),
             pch = 21, size = 2, fill = "white", stroke = 0.5) +
  geom_ribbon(aes(ymin = med_sal - sd_sal,
                  ymax = med_sal + sd_sal,
                  x = date,
                  color = station,
                  fill = station),
              alpha = 0.4, size = 0.1) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_salinity_2m_month.png"),
       width = 16, height = 6, dpi = 300)
```

```{r}
ctd %>% 
  filter(pres == 2 & year > 2014) %>% 
  ggplot(aes(x = as.factor(year), y = sal, color = station, fill = station)) +
  geom_boxplot(alpha = 0.3) +
  geom_point(aes(color = station, fill = station), 
             position = position_dodge(width = 0.75),
             alpha = 0.4) +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_salinity_2m_annual_boxplot.png"),
       width = 16, height = 6, dpi = 300)
```
```{r}
ctd %>% 
  filter(pres == 2 & year > 2014) %>% 
  ggplot(aes(x = as.factor(year), y = sal, color = station, fill = station)) +
  geom_boxplot(alpha = 0.3) +
  geom_point(aes(color = station, fill = station), 
             position = position_dodge(width = 0.75),
             alpha = 0.4) +
  facet_grid(season ~ ., scales = "free_x") +
  ggsci::scale_color_aaas() +
  ggsci::scale_fill_aaas() +
  labs(y = "Salinity") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_salinity_2m_annual_boxplot_season.png"),
       width = 16, height = 14, dpi = 300)
```

```{r}
ctd %>% 
  filter(pres == 2 & year > 2014) %>% 
  group_by(date, station) %>% 
  summarise(temp = mean(temp)) %>% 
  ungroup() %>% 
  ggplot(aes(x = date, y = temp, color = station)) +
  geom_line(size = 1.5) +
  geom_point(pch = 21, size = 2, fill = "white", stroke = 0.5) +
  ggsci::scale_color_aaas() +
  labs(y = "Temp") +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.85, 0.1),
        panel.spacing = unit(3, "lines"))

ggsave(here("figures", "timeseries_temp_2m_raw.png"),
       width = 16, height = 6, dpi = 300)
```

```{r}
#How well does buoy CTD match with field CTD?

ctd_dm %>% 
  rename(sal_ctd = sal) %>% 
  left_join(b_less) %>% 
  filter(sal > 15) %>% 
  ggplot(aes(x = sal_ctd, sal)) +
  geom_point()

#I theory should be spot on.
#Likely off because:

#Including some bad data;
#different depths;
#joining based on daily average of the buoy data and probably a lot of daily variability. Need to join by time. 
```

```{r}
#How well does salinity align with river discharge over this period? Do my relationships hold?
r_less <- r_less %>% 
  mutate(q_b0 = zoo::rollmeanr(lag(q, 0), k = 10, fill = NA),
         q_b1 = zoo::rollmeanr(lag(q, 1), k = 10, fill = NA)) 

sal_riv <- ctd_dm %>% 
  left_join(r_less)

sal_riv %>% 
  ggplot(aes(x = sal, y = q_b1)) +
  geom_point()


```









